Continual NLU: Enabling language models to learn downstream tasks in a continual way

### 2020-03-25 proposal/proposal.tex
modified:   proposal/proposal.bbl 	modified:   proposal/proposal.bib 	modified:   proposal/proposal.tex

\title{Life-long NLU: Continual Learning of Downstream NLU Tasks}

@@

Natural cognitive systems gradually forget previously learned information unlike the catastrophic forgetting observed in current connectionist approaches \cite{french1999catastrophic}. This problem is significant in the domain of natural language understanding (NLU) as well.  Learning a new NLU task without forgetting previous task(s) is a significant problem that needs to be mitigated to achieve general linguistic intelligence. Experiments in Yogatama et al. [2] show that current state-of-the art (SOTA) language models like BERT \cite{DBLP:journals/corr/abs-1810-04805} still require considerable fine tuning on each task before they perform well. They suffer from catastrophic forgetting when trained on multiple tasks in a continual learning (CL) fashion.   Our goal in this work is to address this challenge and investigate approaches to mitigate the catastrophic forgetting problem.

@@

\section{Data}
We propose to work in three phases, as follows:
\begin{itemize}
  \item \textbf{First Phase (Two low data tasks):} Microsoft Research Paraphrase Corpus (MRPC) (3.7k/1.7k) (paraphrase) and Recognizing Textual Entailment (2.5k/3k) (NLI)
  \item \textbf{Second Phase (Two high data tasks):} Quora Question Pairs and Mutli Natural Language Inference. 
  \item \textbf{Final Phase (All tasks):} More than two GLUE tasks (to be chosen later).
\end{itemize}

>>>>

\title{Continual NLU: Enabling language models to learn downstream tasks in a continual way}

@@

Natural cognitive systems gradually forget previously learned information unlike the catastrophic forgetting observed in current connectionist approaches \cite{french1999catastrophic}. This problem is significant in the domain of natural language understanding (NLU) as well.  Learning a new NLU task without forgetting previous task(s) is a significant problem that needs to be mitigated to achieve general linguistic intelligence. Experiments in Yogatama et al. \cite{DBLP:journals/corr/abs-1901-11373} show that current state-of-the art (SOTA) language models like BERT \cite{DBLP:journals/corr/abs-1810-04805} still require considerable fine tuning on each task before they perform well. They suffer from catastrophic forgetting when trained on multiple tasks in a continual learning (CL) fashion.   Our goal in this work is to address this challenge and investigate approaches to mitigate the catastrophic forgetting problem.

@@

\section{Data}
We propose to work in three phases, as follows:
\begin{itemize}
  \item \textbf{First Phase (Two low data tasks):} Microsoft Research Paraphrase Corpus (training - 3700 / testing - 1700) (paraphrase) and Recognizing Textual Entailment (training - 2500 / testing - 3000) (NLI).
  \item \textbf{Second Phase (Two high data tasks):} GLUE: Quora Question Pairs and MutliNLI.
  \item \textbf{Final Phase (All tasks):} More than two GLUE tasks (to be chosen later).
\end{itemize}
